---
title: "CLASS OBSERVATION REPORT"
author: "SCHOOL OF PROFESSIONAL STUDIES"
output: html_document
params:
  class: NA
  section: NA
  obser: NA
  obsee: NA 
  date: NA 
  start: NA
  arrival: NA 
  topic: NA 
  mod: NA
  Qs1: NA
  Qs2: NA
  Qs3: NA
  Qs4: NA
  Qs5: NA
  Qs6: NA
  Qs7: NA
---


```{r,echo=FALSE}
# The `params` object is available in the document.
cat(paste0("I, ", params$obser,", observed Professor ", params$obsee,"'s class on ", params$date,                          ", in the form of ",params$mod, " class. ", "I entered the session at ", params$arrival,
       ", while the class started at ", params$start, ". The class is ", params$class," at section ",
      params$section, " in MS in Management and Systems", " of New York University. The topic covered was ",
       params$topic, ". The following is my in-depth", " evaluation of this class from seven aspects."))
```

### CLASS MANAGEMENT
```{r, echo=FALSE}
cat(params$Qs1)
```

### COMMUNICATION SKILLS
```{r, echo=FALSE}
cat(params$Qs2)
```

### CONTENT MASTERY, RELEVANCE & DELIVERY
```{r, echo=FALSE}
cat(params$Qs3)
```

### INSTRUCTIONAL MATERIALS
```{r, echo=FALSE}
cat(params$Qs4)
```

### STUDENT ENGAGEMENT
```{r, echo=FALSE}
cat(params$Qs5)
```

### USE OF LEARNING MANAGEMENT SYSTEM (LMS)
```{r, echo=FALSE}
cat(params$Qs6)
```

### USE OF THE MEETING TOOL
```{r, echo=FALSE}
cat(params$Qs7)
```


### ADDITIONAL COMMENTS

The professor was very diligent in all communications with the reviewer in setting up the observation date and making the course website available for review.

Signature of Observer:_________________________________________ Date: ___________________________  
Signature of Instructor:_________________________________________ Date: ___________________________